Adaptive Scheduling of Scientific Workflows\\

### 2024-09-30 main.tex
abstract - version 0.0

    \begin{abstract}
        \skug{Fullness score (how much text is available): 0-none to 5 - everything.

        Polishedness score (how well-written is the chapter): 0 messy - 5 very clean.
        }
        TODO: Insert abstract
    \end{abstract}

@@

@@

    \section{Related work: \skug{Full: 4, Polished: 0}}

>>>>

    \begin{abstract}

        Scheduling scientific workflows is important. (\skug{can't imagine a good first sentence})
        They are often represented as directed acyclic graphs (DAGs),
        where vertices correspond to tasks and edges represent the dependencies between them.
       % Since these graphs are often large in both the number of tasks and their resource requirements, it is important
       % to schedule them efficiently on parallel or distributed compute systems.
        Typically, each task requires a
        certain amount of memory to be executed and needs to communicate data to its successor tasks.
        The goal is thus to execute the workflow  as fast as possible (i.e., to minimize its makespan) while satisfying the memory constraints.  %and using parallelism to speed up the execution.

        Hence, we investigate adaptive memory-aware scheduling  of DAG-shaped workflows onto heterogeneous platforms where
        each processor can have a different speed and a different memory size.
        We propose a two-step HEFT-inspired heuristic.
        Its first step is to compute the weights of the tasks.
        We suggest three variants: bottom levels as weights, bottom levels with impact of incoming edge weight,
        and weights along the optimal memory traversal.
        In the second step, we try assigning each task to each processors and execute the assignment that
        is feasible with regard to memory size and gives the earliest finishing time to the task.
        Sometimes, data corresponding to edge weights that is stored in the memory needs to be evicted in order to
        assign a task to a processor.
        We suggest two eviction strategies - largest files first and smallest files first.

        Our experimental evaluation on real-world workflows and simulated (\skug{generated? They are generated from real-world wfs})
        ones with real task and edge weights with up to 30,000 tasks shows that
        respecting memory constraints only costs $11\%$ of runtime in comparison to a non memory-aware baseline.
        Calculating task weights with the impact of memory gives a $x\%$ better makespans on a normal and $y\%$ better makespans
        on small one.
        Calculating task weights along the optimal memory traversal gives on average $z\%$ worse makespans, but improves
        average memory utlization by $t\%$.

    \end{abstract}

@@

    \skug{Fullness score (how much text is available): 0-none to 5 - everything.

    Polishedness score (how well-written is the chapter): 0 messy - 5 very clean.
    }
    TODO: Insert abstract

@@

    \section{Related work: \skug{Full: 5, Polished: 4}}
